\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
innovative aspects (by gerhard), changes to state of the art as requested by tutor (by messi)

\subsection{Innovative aspects}
The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new. In Africa there is a project to do a basic doctor consultation by SMS. The reason for this is because nothing is spread that widely other than a simple mobile phone. Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation. Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}). Combining all the existing programs to one big socialized game for healthier living could even change economy.

@@

@@

\subsection{Socialisation of Healthcare}
\label{sect:star:social}
Another way of motivating people to live healthier and doing their regular workout is to add a social component to the expierence of making sport. The goal of this approach is to create a social network where you can track your own success and compare it to the progress of your friends.

@@

\subsection{Approach of this Project}
This project does not follow the same approach as the above mentioned Social Plattforms or Game Consoles.

Both mentioned approaches are combining their plattform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\

>>>>

\subsection{Innovative aspects}
%The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new. In Africa there is a project to do a basic doctor consultation by SMS. The reason for this is because nothing is spread that widely other than a simple mobile phone. Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation. Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}). Combining all the existing programs to one big socialized game for healthier living could even change economy.

As described in the sections above, there are many different standalone solutions/products in the area of technical-backed healthcare. Our study aims at investigating the possibility of combining them to a whole single system which would lead to a gain in additional value. For the resulting system that means, that the user should not be forced to download and install several different apps or helpers (s)he wants to use, but get provided with one single interface which allows to benefit from it at least as much as if every single application would have been used separately by the user.

Another innovative aspect is the attempt to keep the user interface as much out of the way of the user as possible. User interface design could step at a new higher level, where less commands are necessary to get more information and benefit out of the system. We want to search for and present new ground-breaking methods in user interface design for use in ubiquitous software systems.

@@

Games using these features are e.g. ``Yoga'', EA Sports ``Active 2'' or the game compilation ``Wii Sports''. \\

@@

\subsection{Socialisation of Healthcare}
\label{sect:star:social}
Another way of motivating people to live healthier and doing their regular workout is to add a social component to the expierence of making sport. The goal of this approach is to create a social network where you can track your own success and compare it to the progress of your friends. This area combines knowledge from psychology, social studies and the corresponding behaviour of human beings reacting to such social structures like social networks.

@@

\subsection{Approach of this Project}
This project does not follow the same approach as the above mentioned Social Platforms or Game Consoles.

Both mentioned approaches are combining their platform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\
